\documentclass{exam}

\newcommand\myroot{../..}
\usepackage[quiz]{\myroot/brains8}

\title{Course Syllabus, \mobeardCourseTerm}
\author{\mobeardInstructorShort}
\date{\today}
%\duedate{TBD}

\begin{document}
\maketitle

\begin{questions}
\question \textbf{Sheep brain dissection.} \printdate{7/11/2022}. Gross neuroanatomy. Lab coat and goggles will be provided though you may wish to wear something comfortable that can get dirty. No open-toed shoes. People with long hair may wish to tie it back. 
\question \textbf{Neurons in general.} \printdate{7/12/2022}.  Comparative anatomy of brains and nervous systems, distribution of nerves across animal groups. Neuron form and function, diffusion, facilitated diffusion, active transport across cell membranes, resting potential, and introduction to action potentials.
\question \textbf{Sensory systems, cow eye dissection.} \printdate{7/13/2022}. Examination of the form, function, and evolution of a sensory system (eyes). Make models of intermediate steps in eye evolution. Lab coat and goggles will be provided though you may wish to wear something comfortable that can get dirty. No open-toed shoes. People with long hair may wish to tie it back. 
\question \textbf{Motor neurons and muscle, electrophysiology measurements of a human reflex arc.} \printdate{7/14/2022}. How muscle works and introduction to muscles. Introduction to the reflex arc. You may want to wear something loose and comfortable, e.g. gym shorts, sweatpants, that will allow you to attach a sticky electrode to your knee and thigh. 
\question \textbf{Sensorimotor integration.}\printdate{7/15/2022}. In this session we will put together all we have learned in examining sensorimotor integration. Lab coat and goggles will be provided though you may wish to wear something comfortable that can get dirty. No open-toed shoes. People with long hair may wish to tie it back. 
\end{questions}
\end{document}


